---
title: "Assignment 4"
author: "Abi"
date: "2022-10-30"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing DEA Analysis

## Required Packages
```{r}
library(Benchmarking)
```
```{r}
Data <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5", "Facility 6",
                150,400,320,520,350,320,
                0.2,0.7,1.2,2.0,1.2,0.7,
                14000,14000,42000,28000,19000,14000,
                3500,21000,10500,42000,25000,15000), ncol=5, byrow=F)
colnames(Data) <- c("DMU", "Staff_Hours_Per_Day","Supplies_Per_Day","Reimbursed_Patient_Days","Privately_Paid_Patient_Days")
table<- as.table(Data)
table
```
## Reading Input Data
```{r}
Ip <- matrix(c(150, 400, 320, 520, 350, 320,
                    0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol=2) # Defining inputs
Op <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000,
                    3500, 21000, 10500, 42000, 25000, 15000), ncol=2) # Defining outputs
# Defining column names
colnames(Ip)  <- c("Daily Staff Hours", "Daily Supplies Cost") 
colnames(Op) <- c("Reimbursed Patient-Days", "Privately-Paid Patient Days")
Ip
Op
```
## Creating DEA Analysis Function

To avoid code repetition, let's define a function that will perform the DEA under the given assumption.
```{r}
Analyze_DEA <- function(assumption) {
  analysis <- dea(Ip, Op, RTS=assumption)
  print(eff(analysis))
  print(peers(analysis))
  print(lambda(analysis))
}
```
After obtaining the DEA assumption to use, the function prints out the efficiencies, peers, and lambdas when we call it.

## Performing DEA Analysis
Now, in the following order: FDH, CRS, VRS, IRS, DRS, and FRH, we execute DEA on each of the six assumptions using the function we defined before.

## Free Disposability Hull
```{r}
Analyze_DEA("FDH")
```
## FDH observation

The DMUs are all effective. This is mainly because the FDH technique adheres to a certain principal, which allows it to identify even a very low level of efficiency.

## Constant Return to Scale
```{r}
Analyze_DEA("CRS")
```
## CRS Observations 

We are able to observe the effectiveness of Facilities 1, 2, 3, and 4.

Additionally, we learn that the ineffective facilities Facility 5 and Facility 6 have Facility 1, Facility 2, and Facility 4 as peer members.

Facility 6 is 86.75% efficient, leaving 13.25% inefficient, while Facility 5 is 97.75% efficient, leaving 2.25% inefficient.

## Varying Return to Scale
```{r}
Analyze_DEA("VRS")
```
## VRS observation

We are given the opportunity to observe the effectiveness of Facilities 1, 2, 3, 4, and 5.

In addition, we learn that Facility 6, the alone inefficient facility,and its peer member of Facilities are 1, 2, and 5.

Facility 6 has an efficiency of 89.63%, leaving a 10.37% inefficiency.

## Increasing Return to Scale
```{r}
Analyze_DEA("IRS")
```
## IRS Observation

We are given the opportunity to observe the effectiveness of Facilities 1, 2, 3, 4, and 5.

In addition,Facility 1, Facility 2 and Facility 5 are the peer members for Facility 6 which is the only inefficient facility.

Facility 6 has an efficiency of 89.63%, leaving a 10.37% inefficiency.

## Decreasing Return to Scale
```{r}
Analyze_DEA("DRS")
```
## DRS Observation

We are able to observe the effectiveness of Facilities 1, 2, 3, and 4.

In addition, we learn that the ineffective facilities, Facility 5 and Facility 6, have Facility 1, Facility 2, and Facility 4 as peer members.

Facility 6 is 86.75% efficient, leaving 13.25% inefficient, whereas Facility 5 is 97.75% efficient, leaving 2.25% inefficient.


## Free Replicability Hull
```{r}
Analyze_DEA("ADD")
```
## FRH Observation

The DMUs are all effective. Because it adheres to the no convexity assumption, the output is protected against disposal and reproduction.

## Summary of Results (Inefficient DMUs)
```{r}
Data.summarise.inefficient <- matrix(c("CRS","DRS","IRS","VRS","FDH","FRH",
2,2,1,1,0,0,
"Facility 5 & 6", "Facility 5 & 6","Facility 6", "Facility 6", "-","-",
"97.75% & 86.7%","97.75% & 86.7%","89.63%","89.63%","-","-",
"Facility 1, 2 & 4","Facility 1, 2 & 4","Facility 1, 2 & 5","Facility 1, 2 & 5","-","-",
"0.2, 0.08, 0.54 and 0.34, 0.4, 0.13", "0.2, 0.08, 0.54 and 0.34, 0.4, 0.13", "0.4, 0.34 and 0.26", "0.4, 0.34 and 0.26", "-","-"),ncol=6,byrow=F)

colnames(Data.summarise.inefficient) <- c("RTS","Count_Inefficient_DMUs","Name_DMUs","%_Inefficiency","Peers","Lambda")

as.table(Data.summarise.inefficient)
```
## Summary of Results (Efficient DMUs)
```{r}
Data.summarise.efficient <- matrix(c("CRS","DRS","IRS","VRS","FDH","FRH",
"Facility 1, 2, 3 & 4","Facility 1, 2, 3 & 4","Facility 1, 2, 3, 4 & 5", "Facility 1, 2, 3, 4 & 5", "All DMUs", "All DMUs"), ncol = 2, byrow=F)
colnames(Data.summarise.efficient) <- c("RTS", "Efficient_DMUs")
as.table(Data.summarise.efficient)
```
Under all six assumptions, facilities 1, 2, 3, and 4 are considered efficient, and without the assumption of convexity all six facilities are efficient. 

Under the VRS and IRS assumptions, facility 6 is inefficient. Its peers are facilities 1, 2, and 5 with $\lambda_1^6 = 0.401$, $\lambda_2^6 = 0.342$, and $\lambda_5^6 = 0.256$.

Under the CRS and DRS assumptions, facilities 5 and 6 are both inefficient. The peers of both facilities 5 and 6 are facilities 1, 2, and 4, with $\lambda_1^5 = 0.2$, $\lambda_2^5 = 0.080$, $\lambda_3^5 = 0.538$, $\lambda_1^6 = 0.343$, $\lambda_2^6 = 0.395$, and $\lambda_3^6 = 0.131$.

## Plotting Graph

## FDH Plot
```{r}
dea.plot(Ip,Op,RTS="FDH")
```

## VRS Plot
```{r}
dea.plot(Ip,Op,RTS="VRS")
```

## CRS Plot
```{r}
dea.plot(Ip,Op,RTS="CRS")
```

## ADD Plot
```{r}
dea.plot(Ip,Op,RTS="ADD") 
```

DRS Plot
```{r}
dea.plot(Ip,Op,RTS="DRS") 
```
IRS Plot
```{r}
dea.plot(Ip,Op,RTS="IRS") 
```

 

