---
title: "Assignment 3"
author: "Abi"
date: "2022-10-15"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

$$
\text{The objective function is }Min\hspace{.3cm} Tc= 622x_{11}+614x_{12}+630x_{13} + 641x_{21}+645x_{22}+649x_{23}
$$
Supply Costraints:
$$
x_{11}+x_{12}+x_{13} \le 100 \\
x_{21}+x_{22}+x_{23} \le 120 
$$
Demand Constraint:
$$
x_{11}+x_{21} \ge 80 \\
x_{12}+x_{22} \ge 60 \\
x_{13}+x_{23} \ge 70 
$$
Non-Negative:
$$
x_{i,j} \ge 0
$$
```{r}
library(lpSolve)
```

```{r}
Problem <- matrix(c(22,14,30,600,100,
                16,20,24,625,120,
                80,60,70,"-","-"),ncol = 5,byrow = TRUE)
colnames(Problem)<- c("Warehouse1","Warehouse2","Warehouse3","Production Cost","Production Capacity")
rownames(Problem)<-c("Plant A","Plant B","Monthly Demand")
Problem <-as.table(Problem)
Problem
```
```{r}
# Since production and demand is unbalanced, Dummy column is created

# Name of the column and rows:
costs <- matrix(c(622,614,630,0,
                  641,645,649,0),ncol = 4,byrow = TRUE)
colnames(costs)<- c("Warehouse1","Warehouse2","Warehouse3","Dummy")
rownames(costs)<-c("Plant A","Plant B")
costs <-as.table(costs)
costs

# Setting up the row signs and production capacity values
row.signs <- rep("<=",2)
row.rhs<- c(100,120)

# Setting up the column sign and demand values
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)
```

```{r}
# Running lptrans to find minimum cost

lptrans <- lp.transport(costs,"min",row.signs,row.rhs,col.signs,col.rhs)

# Values of all variables
lptrans$solution
```

```{r}
# Objective function 
lptrans$objval

```
# Therefore 

# x12 = 60

# x13 = 40

# x21 = 80

# x23 = 30

# Objective function is 132790.

2) Dual Problem:

Formulating the dual constraints and variables
$$
\text{The objective function is }Max\hspace{.3cm} VA= 80w_{1}+60w_{2}+70w_{3}-100p_{1}-120p_{2}
$$
$$
\text{Where,}\hspace{.3cm}w_{1}\text{= Price received at the Warehouse 1}
$$
$$
w_{2}\text{= Price, received at the Warehouse 2}
$$
$$
w_{3}\text{= Price, received at the Warehouse 3}
$$
$$
p_{1}\text{= Price, purchased at the Plant A}
$$
$$
p_{2}\text{= Price, purchased at the Plant B}
$$
Subject to:
$$w_{1}-p_{1} \ge 622$$
$$w_{2}-p_{1} \ge 614$$
$$w_{3}-p_{1} \ge 630$$
$$w_{1}-p_{2} \ge 641$$
$$w_{2}-p_{2} \ge 645$$
$$w_{3}-p_{2} \ge 649
$$
3) Economic Interpretation of dual:

 The goal of AED's business is to reduce the total cost of production and shipment.

 To achieve this, the corporation needs hire a logistic company to handle the transportation, which will include purchasing the AEDs and transporting them to various warehouses in an effort to reduce the overall cost of production and shipping.

$$
\text{The constraints in the dual can be modified as}$$
$$w_{1} \ge 622+p_{1}$$
$$w_{2} \ge 614+p_{1}$$
$$w_{3} \ge 630+p_{1}$$
$$w_{1} \ge 641+p_{2}$$
$$w_{2} \ge 645+p_{2}$$
$$w_{3} \ge 649+p_{2}
$$
$$ \text{From the above we get to see that}\hspace{.3cm} w_{1}−p_{1}\ge 622$$
$$ \text{That can be exponented as}\hspace{.3cm} w_{1} \ge 622+p_{1}$$
$$ \text{Here}\hspace{.3cm} w_{1}\hspace{.3cm}\text{is considered as the price payments being received at the origin which is nothing else,but the revenue,whereas}\hspace{.3cm} p_{1}+622\hspace{.3cm}\text{is the money paid at the origin at PlantA}
$$
$$\text{This can be formulated as below}\\
MR \ge MC
$$

$$
\text{If MR < MC, in order to meet the Marginal Revenue (MR), we need to decrease the costs at the plants.}$$
$$\text{If MR > MC, in order to meet the Marginal Revenue (MR), we need to increase the production supply.}$$
$$\text{For a profit maximization, The Marginal Revenue(MR) should be equal to MarginalCosts(MC)}$$
$$\text{Therefore, MR=MC}$$
$$\text{Based on above interpretation, we can conclude that,profit maximization takes place if MC is equal to MR.}
$$


